1-methods-toys

### 2017-12-05 analysis/analyses/evaluate_toy/1-methods-toys.Rmd
score rules

```{r}
library(tidyverse)
library(dyntoy)
library(dyneval)

@@

tasks <- generate_toy_datasets(num_replicates = 1, num_cells=300)
```

```{r}
tasks$counts <- map(tasks$counts, function(counts) {
  cbind2(counts, matrix(sample(1:100, nrow(counts)*100, replace=TRUE), nrow=nrow(counts))) %>% {magrittr::set_colnames(., paste0("G", 1:ncol(.)))}
})
task <- dynutils::extract_row_to_list(tasks, 2)
pheatmap::pheatmap(task$counts)

source("~/thesis/projects/dynverse/dynmodular/dimred_wrappers.R")
space <- task$counts %>% dimred_dp(2, neigen=2) %>% as.data.frame
# space <- task$counts %>% dimred_mds(2) %>% as.data.frame
# space <- task$counts %>% dimred_lle(2) %>% as.data.frame
space <- space %>% bind_cols(task$cell_grouping %>% slice(match(rownames(task$counts), cell_id)))
space %>%  ggplot() + geom_point(aes(Comp1, Comp2, color=group_id))
```

@@

metric_names <- c("mean_R_nx", "auc_R_nx", "Q_local", "Q_global", "correlation", "isomorphic", "robbie_network_score")

method_names <- c("monocle_ddrtree", "scorpius")
```

@@

  factory(function() {
    dyneval:::execute_evaluation(tasks, method, params, metrics = metric_names, timeout = 99999999999999)
  }
  )()
})
# }, qsub_environment = list2env(lst(method_descriptions, tasks, metric_names, method_params)), qsub_config = PRISM::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```

Gather the output of the different methods, and check whether there were any errors
```{r}
# results <- PRISM::qsub_retrieve(results)
scores <- purrr::map(results, function(.) {
  bind_cols(
    tibble(
      error=list(.$err), 
      warning=list(.$warning), 
      model=attr(.[[1]], "extras")$.models
    ),
    attr(.[[1]], "extras")$.summary
  ) %>% mutate(method_name=.$method_name)
}) %>% bind_rows() %>% mutate(errored = !map_lgl(error, is.null), method_id=rep(method_names, each=nrow(tasks))) %>% dplyr::select(-contains("method_name1"))

>>>>

```{r}
library(tidyverse)
library(dyntoy)
library(dyneval)
library(dynmethods)

@@

data("toy_tasks")
tasks <- toy_tasks
```

```{r}
tasks$counts <- map(tasks$counts, function(counts) {
  cbind2(counts, matrix(sample(1:100, nrow(counts)*100, replace=TRUE), nrow=nrow(counts))) %>% {magrittr::set_colnames(., paste0("G", 1:ncol(.)))}
})
task <- dynutils::extract_row_to_list(tasks, 3)
pheatmap::pheatmap(task$counts)

source("~/thesis/projects/dynverse/dynmodular/dimred_wrappers.R")
# space <- task$counts %>% dimred_dp(2, neigen=2) %>% as.data.frame
space <- task$counts %>% dimred_mds(2) %>% as.data.frame
# space <- task$counts %>% dimred_lle(2) %>% as.data.frame
space <- space %>% bind_cols(task$prior_information$grouping_assignment %>% slice(match(rownames(task$counts), cell_id)))
space %>%  ggplot() + geom_point(aes(Comp1, Comp2, color=group_id))
```

@@

metric_names <- c("mean_R_nx", "auc_R_nx", "Q_local", "Q_global", "correlation")

method_names <- c("scorpius")
```

@@

  # factory(function() {
    dyneval:::execute_evaluation(tasks, method, params, metrics = metric_names, timeout = 100)
  # }
  # )()
})
# }, qsub_environment = list2env(lst(method_descriptions, tasks, metric_names, method_params)), qsub_config = PRISM::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```

Gather the output of the different methods, and check whether there were any errors
```{r}
scores <- purrr::map(results, function(result) {
  bind_cols(
    tibble(
      model = attr(result, "extras")$.models
    ),
    attr(result, "extras")$.summary
  )
}) %>% bind_rows()
